---
title: "Identifying the polypharcology profile of a compound using ChEMBL Bioactivities"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github
runtime: shiny
---
For comments, suggestions and errors, plese contact me at: asegura@ebi.ac.uk
```{r setup, include=FALSE}
library(dplyr)
library(jsonlite)
library(urltools)
library(reticulate)
library(DT)
library(knitr)
library(networkD3)
library(clusterProfiler)
library(ReactomePA)
library(org.Hs.eg.db)
library(visNetwork)
library(tidyverse)
library(heatmaply)
library(XML)
library(shiny)
source_python("make_matrix.py")
source_python("sub_struc.py")
source_python("query_struc.py")
```
# Similarity search using ChEMBL webservices
```{r, echo=FALSE}
fluidRow(
    column(4,
  textInput("my_mol", "Please provide a molecule in SMILES format", "N#Cc1ccccc1Cn3c(N2CCCCC2)cc(=O)[nH]c3=O", width = "600px"),
  verbatimTextOutput("smiles"),
  actionButton("go", "Run"),
  actionButton("reset", "Reset")
    ),
      column(3,
      sliderInput("sim_t", label = "Similarity threshold:", min = 70, max = 100, value = 85, step = 5)
    )
  )
```

# This is your query

```{r}
imageOutput('query_svg')
```


```{r, context="server"}


  output$smiles <- renderPrint({
    input$my_mol
  })
  
baseur_sim <- "https://www.ebi.ac.uk/chembl/api/data/similarity/"



values <- reactiveValues(df_data = NULL)
values2 <- reactiveValues(df_data2 = NULL)
values3 <- reactiveValues(df_data3 = NULL)
values4 <- reactiveValues(df_data4 = NULL)

    observeEvent(input$go,{
      simil_cut_off = paste0("/", as.character(input$sim_t))
      my_compound <- as.character(input$my_mol)
      
      pba <- fromJSON(paste0(baseur_sim, url_encode(my_compound), simil_cut_off, ".json?limit=50"), flatten=TRUE)
      table_comp_match <- pba$molecules[,c(15,23,55,33,21,60)]
      colnames(table_comp_match) <- c("ChEMBL_ID","similarity",
                                "Ro5_violations","withdrawn_info","name","canonical_smiles")

table_comp_match$name <- ifelse(is.na(table_comp_match$name), table_comp_match$ChEMBL_ID, table_comp_match$name)

url_compound <- "https://www.ebi.ac.uk/chembl/beta/compound_report_card/"



table_out_pba <- mutate(table_comp_match, ChEMBL_ID = paste0("<a href='",url_compound,ChEMBL_ID,"' target='_blank'>",ChEMBL_ID,"</a>"))
  

values$df_data <- table_out_pba
    
#####Generating a similarity matrix using Rdkit


values2$df_data2 <- make_matrix(table_comp_match, my_compound)

out_subst <- make_subst(table_comp_match, my_compound)
query_str <- moltosvg(as.character(input$my_mol))

xData <- xmlParse(out_subst)
xquery <- xmlParse(query_str)

saveXML(xData, file = "substr.svg")
saveXML(xquery, file = "query.svg")

values3$df_data3 <- "substr.svg"
values4$df_data4 <- "query.svg"

    
    })

observeEvent(input$reset, {
    values$df_data <- NULL
    values2$df_data2 <- NULL
    values3$df_data3 <- NULL
    values4$df_data4 <- NULL
  })



 output$plot_as_svg  <- renderImage({
   if (is.null(values3$df_data3)) return()
          
   return(list(
            src = values3$df_data3
          ))
       }, deleteFile = TRUE)
 
 output$query_svg  <- renderImage({
   if (is.null(values4$df_data4)) return()
          
   return(list(
            src = values4$df_data4
          ))
       }, deleteFile = TRUE)

output$tbl = DT::renderDT({
  if (is.null(values$df_data)) return()
  DT::datatable(values$df_data, escape = F, rownames = F, caption = "Similarity search results")
  })


output$heatmap = renderPlotly({
  if (is.null(values2$df_data2)) return()
  heatmaply(as.matrix(values2$df_data2), margins = c(40, 40, 0, 0),
          colors = BrBG
          )
  
  })

```


# Similarity search results
```{r}
DTOutput('tbl', width = 500)

```
# Ok, these compunds are similar to my query, but what is the relationship between them?                                                            
### Let's perform a clustering analysis based on the similarity all vs all
```{r}
plotlyOutput('heatmap', width = "900px", height = "900px")
```

# Are the compounds sharing a common sub-structure?

```{r}
imageOutput('plot_as_svg')
```



